### 2021-01-24 README.Rmd
Renamed object class from fe_bayes_lm to comp_bayes_lm
update structure of fitted model
now contains the prior parameters, posterior parameters, and the formula object.

renames posterior_param_ex -> comp_bayes_lm_ex

```{r}
# Fit model
posterior_param_ex <- focal_vs_comp_ex %>%
  fe_bayes_lm(prior_param = NULL, run_shuffle = FALSE)

# Get predicted dbh values values
predictions <- focal_vs_comp_ex %>%
  predict(posterior_param = posterior_param_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

@@

# Plot posteriors
plot_ex <- posterior_param_ex %>%
  plot_bayesian_model_parameters()
plot_ex[["lambda"]]
```

>>>>

```{r}
# Fit model
comp_bayes_lm_ex <- focal_vs_comp_ex %>%
  comp_bayes_lm(prior_param = NULL, run_shuffle = FALSE)

# Get predicted dbh values values
predictions <- comp_bayes_lm_ex %>%
  predict(focal_vs_comp = focal_vs_comp_ex) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

@@

# Plot posteriors
comp_bayes_lm_ex %>%
  autoplot(type = "intercepts")
comp_bayes_lm_ex %>%
  autoplot(type = "dbh_slopes")
comp_bayes_lm_ex %>%
  autoplot(type = "competition")
```
